MLH1 Results Outline

### 2020-02-15 doc/Results.rmd
starting checking the SC_skel algorithim output

#skeletonize
SC.skel = read.csv("~./SC_skeletonize/data/SCskel_output_nov19.csv", header = TRUE, strip.white = TRUE)

@@

color_chrm_class <- c( '0' = "#00BFC4", '1' = "#7CAE00", '2' = "#F8766D", '3' = "#C77CFF")

@@

```{r totSC_setup, echo=FALSE}
#SC.skel
#"anon.batch" "rand_name"  "bin_size"   "skel_size"

#MERGEING MLH1 with SKEL
MLH1.merge.Skel <- merge(original_DF, SC.skel, by.x = "Random.Name", by.y = "rand_name", all= F)
OG.MLH1.merge.Skel <- MLH1.merge.Skel #raw version of DF

MLH1.merge.Skel <- add_mouse(MLH1.merge.Skel)
MLH1.merge.Skel <- add_strain(MLH1.merge.Skel)
MLH1.merge.Skel <- add_sex(MLH1.merge.Skel)
MLH1.merge.Skel <- add_subsp(MLH1.merge.Skel)
MLH1.merge.Skel <- add_category(MLH1.merge.Skel)
MLH1.merge.Skel <- add_subsp(MLH1.merge.Skel)

@@

MLH1.merge.Skel$bin_size <- as.numeric(MLH1.merge.Skel$bin_size)
MLH1.merge.Skel$skel_size <- as.numeric(MLH1.merge.Skel$skel_size)

#table(MLH1.merge.Skel$category)

!Note! the most recent tot.sc csv was missing ~2 batches... rerun

@@

tot.sc <- ggplot(data= MLH1.merge.Skel, aes(y = bin_size, x=mouse))+ geom_point()
tot.sc2 <- ggplot(data= MLH1.merge.Skel, aes(y = skel_size, x=mouse))+ geom_point()

#seems like the outliers have been removed
```

@@

```{r show.tot.sc, echo=FALSE}

>>>>

#skeletonize
SC.skel = read.csv("~./SC_skeletonize/data/SCskel_output_feb20.csv", header = TRUE, strip.white = TRUE)

@@

color_chrm_class <- c( '0' = "#00BFC4", '1' = "#7CAE00", '2' = "#F8766D", '3' = "#C77CFF", '4'= "#F564E3")
#4!!

show_col(hue_pal()(5))

@@

```{r totSC_setup, echo=FALSE}
#SC.skel
#"anon.batch" "rand_name"  "bin_size"   "skel_size" , all batches included

SC.skel.OG <- SC.skel #5683

#MERGEING MLH1 with SKEL
MLH1.merge.Skel <- merge(original_DF, SC.skel, by.x = "Random.Name", by.y = "rand_name", all= F)

MLH1.merge.Skel <- add_mouse(MLH1.merge.Skel)
MLH1.merge.Skel <- add_strain(MLH1.merge.Skel)
MLH1.merge.Skel <- add_sex(MLH1.merge.Skel)
MLH1.merge.Skel <- add_subsp(MLH1.merge.Skel)
MLH1.merge.Skel <- add_category(MLH1.merge.Skel)
MLH1.merge.Skel <- add_subsp(MLH1.merge.Skel)
#5110,

OG.MLH1.merge.Skel <- MLH1.merge.Skel #raw version of DF

#check for DUPs, #check for duplicatations of the random name
MLH1.merge.Skel$ fileName  <- as.character(MLH1.merge.Skel$fileName)
tot.SC.dupies <- MLH1.merge.Skel[duplicated(MLH1.merge.Skel$ fileName ),]

@@

MLH1.merge.Skel$bin_size <- as.numeric(MLH1.merge.Skel$bin_size)
MLH1.merge.Skel$skel_size <- as.numeric(MLH1.merge.Skel$skel_size)
#table(MLH1.merge.Skel$category)

#remove outliers
MLH1.merge.Skel <- MLH1.merge.Skel  %>% filter(bin_size < 60000)

@@

tot.sc <- ggplot(data= MLH1.merge.Skel, aes(y = bin_size, x=strain))+ geom_jitter()+facet_wrap(~category, scales = "free")

#seems like the outliers have been removed

MLH1.merge.Skel.wsb.male <- MLH1.merge.Skel  %>% filter(category < "WSB male" )

tot.sc.wsb.male <- ggplot(data= MLH1.merge.Skel.wsb.male, aes(y = bin_size, x=strain))+ geom_jitter()+facet_wrap(~category, scales = "free")

tot.sc.single.male <- ggplot(data= MLH1.merge.Skel  %>% filter(category == "G female" ) , aes(y = bin_size, x=strain))+ geom_jitter()+facet_wrap(~category, scales = "free")

Checking the outliers at category level,

WSB male,
10apr15_31mar15_WSB_m3_sp1_4_rev.tif

G outliers, 
G 19oct15_12oct15_G_m1_sp1_17.1_rev.tif

LEW, low outlier, 
6mar18_1feb18_LEW_m1_sp1_21.5_rev

PWD outliers, 6mar15_1mar15_PWD_m1_sp4_6.1_rev.tif, 7mar15_1mar15_PWD_m1_sp4_2_rev.tif, and 20jul15_18may15_PWD_m2_sp1_10.2_rev.tif

G female; 1mar16_20feb16_G_f3_sp1_8_rev.tif and 21nov16_16jan16_G_f2_sp1_15_rev.tif

@@

Total SC

```{r show.tot.sc, echo=FALSE}
totSC.mouse.av.table <- totSC.mouse.av.table %>% filter(strain!="CAST" & strain !="F1"& strain !="SPIC" & strain !=  "CAROLI" & strain !="SPRET"& strain !="HMI"& strain !="PERC")
